\chapter*{Abstract}

Problems incorporating both solid-fluid and solid-solid interactions are prevalent in a large number of engineering disciplines. A fairly established numerical scheme to model solid-solid interactions is that of the Discrete Element Method (DEM). Further, recent attempts to use Meshfree Particle Methods such as Smoothed Particle Hydrodynamics (SPH) for fluid flow problems have shown encouraging results.

Traditional Eulerian approaches for obtaining the flow field information suffer on account of having to accurately capture and keep track of the complicated solid-fluid interfaces. Furthermore, implementing DEM in Eulerian frameworks, although possible, is tedious. Both the DEM and SPH, being particle methods, are good candidates for integration, whence a robust and fully Lagrangian formulation can be realised. PySPH, an open source Python based framework to perform Smoothed Particle Hydrodynamics simulations, being notoriously user and developer friendly is the tool used for achieving the integration.

The present work first elucidates the SPH and DEM numerical methods, followed by a description of the structure of the PySPH framework. Therafter, a simple DEM based Rigid Body Collision Model, its Proof of Concept implementation in PySPH and a numerical validation study is detailed; it is followed by the description of an optimized collision model based on recent research endeavours. Finally the algorithm developed for the optimized model and its implementation in PySPH is discussed.
