\chapter*{Acknowledgments}

My time at the Centre was underscored by innumerable priceless encounters with a number of inspirational individuals. I am glad that I have a opportunity to express my gratitude for their invaluable contributions.

First and foremost, a big thank you to Dr. Prabhu Ramachandran of the Department of Aerospace Engineering at IIT Bombay. Not only has he been instrumental in introducing me to a unique and challenging topic to pursue as part of my Masters Project, but he has also always available to mentor, guide and advise me; this, despite the obvious constraints of distance, personal and professional commitments and a visibly jam-packed schedule. My interactions with Prabhu Sir have always helped me to see things in fresh light; it was really a pleasure to have had the opportunity to work and interact with him.

Another large, ubiquitous calming presence at CMS was that of Dr. Sukratu Barve. The knowledge that I could always bank on Barve Sir for academic and/or other kinds of guidance was very reassuring. As my Guide at CMS, we had countless fruitful discussions, many of which continued well past normal office hours. My heartfelt gratitude for all his suggestions, comments and insights.

Further notable mentions are that of Dr. Mihir Arjunwadkar and Dr. Jayaraman Valadi. Mihir Sir has been kind and encouraging from the very beginning. Conversations with him would always be candid and at the same time extremely enlightening and motivating. Jayaraman Sir, with his vast experience, brought to the table a wealth of knowledge. Any interaction with him left me knowing a little more than I had before. Thanks to them, monotonously mundane days became enjoyable.

Finally, my friends (you know who you are), my sisters, Drs. Mallika and Manjari Jonnalagadda, my brothers-in-law, Saju Jospeh and Shantanu Ozarkar and my parents, Kedarnath and Rama Jonnalagadda have been a pillar of support through thick and thin. It is only with their love and support that I could be in a position to successfully complete this endeavour. Also, an eternal source of joy in those inevitable times of stress came in the shape and form of my nephews Siddhartha and Anay; they too have played a big role in their own little way.

\vfill
\noindent
{\large{Copyright \copyright \space 2016 | Anirudh Jonnalagadda\\All rights reserved}}
